\textbf{Volatility and the Buyback Anomaly}

### 2016-05-12 manuscriptJF.Rnw
tool update + copyright
latex

source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
source("../FinanceLibraries/latex_code.R")
source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
source("Paper_global_parameters.R")

>>>>

source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
source("interactive_tool_files/latex_code.R")
source("interactive_tool_files/ff_industries_sic.R")
source("Paper_global_parameters.R")
